%-------------------------
% Resume in LateX
% Author : Sathwik Aileneni
% License : MIT
%------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Define a custom color for role names
\definecolor{rolecolor}{RGB}{0, 90, 150}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\normalsize
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{\textit{\small\color{rolecolor}#3}} & \textbf{\textit{\small #4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\textit{\small\color{rolecolor}#1}} & \textbf{\textit{\small #2}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/sathwik-aileneni}{\Large Sathwik Aileneni}} & Email: \href{mailto:cwsathwik@gmail.com}{cwsathwik@gmail.com}\\
  \href{https://github.com/sathwik-aileneni}{github.com/sathwik-aileneni} & Mobile: \href{tel:+918123708676}{+91-8123708676} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Institute of Information Technology (IIIT-H)}{Hyderabad, India}
      {Bachelor of Technology in Computer Science and Engineering}{2015 -- 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Plivo Communications Private Limited.}{Bangalore, India (Remote)}
      {Senior Software Engineer}{Jan 2023 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{Reporting Infrastructure}
          {Explored multiple solutions for user-facing reporting by running POCs with ClickHouse and Explo, identifying limitations and performance gaps. Implemented \underline{DBT} for scalable, low-latency data transformation, \underline{reducing query time from 8 seconds to a max of 100ms}.}
        \resumeItem{System Reliability \& Performance}{
          \begin{itemize}[label=$\circ$]
            \item Identified and mitigated a major idempotency issue in Celery when used with Redis, where a bug caused messages to be duplicated indefinitely. Revamped and Implemented a robust workaround within strict deadlines that \underline{limited duplication to a controlled maximum of six, and idempotent execution}.
            \item Optimized job execution in a distributed worker system by introducing a concurrent temporary execution registry on the fly to prevent duplicate job processing and generalized it with an added observability mechanism for real-time tracking.
            \item Led AWS optimizations, segregating not so CPU or Memory Intensive to a new cluster with a smaller ECR image, resulting in improved system performance and \underline{reduced costs by 10\%}.
            \item Set up traceability and alerting systems using prometheus, opentelemtry and sentry, reducing the Mean Time To Detection (MTTD) for incidents by 30\%.
          \end{itemize}
        }
        \resumeItem{Team Leadership}
          {Managed and mentored a team of five engineers, delegating tasks, breaking down major deliverables into subtasks, and parallelizing efforts to meet deadlines for support and feature requests. Also introduced an AI-based PR review system to enhance developer productivity for security issues.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Engineer - 2}{Jul 2021 -- Jan 2023}
      \resumeItemListStart
        \resumeItem{Salesforce Integration}
          {Led the end-to-end Salesforce integration—from ideation, research, and design to implementation—delivering reliable bidirectional sync with custom intervals and achieving near real-time data consistency.}
        \resumeItem{Product Integration}
          {Integrated the acquired platform Decanext (email sequence automation) into Sellular, extending it with SMTP/IMAP support, variable handling, and scheduling—seamlessly connecting it to the in-house CDP (Customer Data Platform) layer.}
        \resumeItem{Performance Optimization}
          {Resolved a critical SQS network issue affecting background message reliability. Implemented a solution using the \underline{transactional outbox pattern to ensure 100\% message persistence}. Led release planning to ensure zero downtime for existing messages, with a phased rollout.}
        \resumeItem{Reliability and Compliance}
          {Improved system reliability by resolving critical production issues within SLA and addressing third-party integration issues. Also implemented security fixes to support SOC2 and GDPR compliance.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Engineer - 1}{Jun 2019 -- May 2021}
      \resumeItemListStart
        \resumeItem{PHLO Features}
          {Delivered core PHLO (Plivo's visual flow builder for call and SMS APIs) features—such as header redirection and multiparty calls—streamlining customer onboarding.}
        \resumeItem{Sellular Development}
          {Chosen as a founding engineer at Sellular, led development of core calling and SMS features, a multichannel notification system (SMS, email, in-app), and customer reports via AWS QuickSight—improving product functionality and usability.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Engineering Intern}{May 2018 -- Jul 2018}
      \resumeItemListStart
        \resumeItem{Automation Framework}
          {Designed and implemented a UI automation framework to streamline sanity and smoke testing, enhancing deployment quality and earning a full-time offer based on outstanding impact.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Python, GoLang (Go), JavaScript}
    \resumeSubItem{Frameworks}
      {Django, Flask, FastAPI, Echo, ReactJS, VueJS, JQuery, Selenium}
    \resumeSubItem{Databases}
      {Postgres, Clickhouse, Elasticsearch, Redis}
    \resumeSubItem{Cloud \& DevOps}
      {AWS, Docker, Jenkins, Github Actions, ELK}
    \resumeSubItem{Others}
      {DBT, Sentry, Prometheus, OAuth, Microservices, CRM Integrations (Salesforce, Hubspot)}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
